Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2016-01-14 docs/appendixB.Rmd
adds year effect to sims; updates docs with Mevin's comments

![Spatial variogram of model residuals showing where spatial dependence disappears (~500 meters; asymptote of the variogram), and the value chosen for the kernal bandwidth in Eq. 6 of the main text (500/3; dashed black line).](../results/avgresidual_variogram_withrange_subset.png)

>>>>

![Spatial variogram of model residuals showing where spatial dependence disappears (~500 meters; asymptote of the variogram), and the value chosen for the kernel bandwidth in Eq. 6 of the main text (500/3; dashed black line).](../results/avgresidual_variogram_withrange_subset.png)
